---
title: "Cleaning the Combined BI And Survey Career Data"
author: "Ri'ann Yates-Miller"
output:
  html_document:
    date: "`r format(Sys.time(), '%d %B, %Y')`"
    code_folding: hide
    df_print: paged
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_float: yes
    code_download: true
  word_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
rm(list = ls()) # clear global environment
graphics.off() # close all graphics
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(DataExplorer,tidyverse,readxl,zoo,stargazer,kableExtra,skimr,plotly,ggpubr,vtable,tm)
```

# Introduction and Purpose

Write something here

# Data Sources

Write something here

## Read in the data

```{r}
data=readRDS(file = "FSB_BI_Survey_2019_2021.rds")
```

# Introductory EDA

Describing each data preprocessing step with small chunks of code, output where necessary, and documentation
```{r}
introduce(data)
```
```{r}
plot_intro(data)
```
```{r}
plot_missing(data)

##Basically I think we should keep: 
# year
# GPA.Range
# maybe major 1
# survey plans
# survey internships
# survey intern one
# maybe survey offers
# survey salary
# maybe survey dept func

# if we are talking salary should we keep a location variable to control for this ?
# Does grades/GPA affect the kind of job offers ? should we control for this ? 
```

Fixing text issues in survey_state 

```{r}
class(data$survey_state)

#the survey_state variables is of type character, need to convert to factor to check levels and model
data$survey_state = as.factor(data$survey_state)
#check the levels 
levels(data$survey_state)
# checking the levels in survey_state
#distinct_levels <- levels(data$survey_state)
#print(distinct_levels)
```

```{r}
#cleaning the observations 
# Convert state names to uppercase for consistency
data$survey_state <- tolower(data$survey_state)

#remove abbreviations
data$survey_state <- gsub("[^a-zA-Z]", "", data$survey_state)

#convert to numerical representations
data$survey_state <- match(data$survey_state, tolower(state.abb))

data$survey_state <- state.name[(data$survey_state)]
print(unique(data$survey_state))
```

```{r}

```


```{r}
install.packages("stringdist")
library(stringdist)
# Define the correct spelling
correct_spelling <- "OH"

# Calculate string distances
distances <- stringdistmatrix(data$survey_state, correct_spelling)

# Find the index of the closest match
closest_match_index <- which.min(distances)

# Replace the closest match with the correct spelling
data$survey_state[closest_match_index] <- correct_spelling

# Check the cleaned data
levels(data$survey_state)

```


```{r}

```

```{r}
plot_bar(data)
```
```{r}
data = data |> 
  dplyr::select(year.x, GPA.Range, major1, survey_plans, survey_internships, survey_internone, survey_offers, survey_salary, survey_deptfunc)

data$survey_internships = as.numeric(data$survey_internships )
data$survey_offers = as.numeric(data$survey_offers)
data$year.x = as.factor(data$year.x)
data$GPA.Range = as.factor(data$GPA.Range)
data$survey_plans = as.factor(data$survey_plans)
data$survey_deptfunc = as.factor(data$survey_deptfunc)
```


```{r}
#dummy endcoding all the variables
```

```{r}
introduce(data)
```
```{r}
plot_intro(data)
```
```{r}
plot_missing(data)
```

```{r}
plot_histogram(data)
```
```{r}
## what do with all the NAs. We cant really do anything with them if we dont have that data --> salary is actually a problem
## possible missing value indicator and imputation??? idk???
```


```{r}
gpa_major_sm = 
  data |> 
  dplyr::group_by(GPA.Range, major1) |>
  dplyr::summarise( 
    internships = mean(survey_internships), 
    offers = mean(survey_offers), 
    salary = mean(survey_salary)
  )
```

```{r}
year_sm = 
  data |> 
  dplyr::group_by(year.x) |>
  dplyr::summarise( 
    internships = mean(survey_internships), 
    offers = mean(survey_offers), 
    salary = mean(survey_salary)
  )
```

```{r}
gpa_major_sm

```
```{r}
year_sm

```


```{r}
## Should we make all the factors dummy for the regression?

#making the dummy's
```

# Data Preprocessing

Describing each data preprocessing step with small chunks of code, output where necessary, and documentation


# The rest of your document

Add sections and subsections as necessary to guide your analysis

